---
title: My dynamic report
output: html_fragment
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo=FALSE, message=FALSE, warning=FALSE, error=FALSE)

```

```{css}
body {
  font-family: Arial;
  line-height: 1.75;
}

h2 {
  color: blue;
}

p {
  font-size: 18px
}
```

## Analysis of Gender, Licence Ownership and Average Speed by observing in Daily Life

This report explores the characteristics of individuals in daily life observations, focusing on gender distribution and licence ownership.
Analysis and summary bar charts and statistics used to better understand the data.

```{r}
library(tidyverse)
logged_data <- read_csv("https://docs.google.com/spreadsheets/d/e/2PACX-1vQdjP0Hl5k6QbgxoYmfEScv7bRRQ9yhn0YRkhL9SagE0ryTqOfB8lgpexDRRsNVVWMFJ0OYteFdUoUa/pub?gid=2105482907&single=true&output=csv")

# Change the name of columns
latest_data <- logged_data %>%
  rename(gender = 2,
         licence = 3,
         average_speed = 4)

# To find how many rows in gender
length(latest_data$gender)

# What is the maximum value in average_speed
max(latest_data$average_speed, na.rm = TRUE)
```
```markdown
There are `r length(latest_data$gender)` sample size totally, which is a little bit small so that cause some bias.

The max average_speed is `r max(latest_data$average_speed, na.rm = TRUE)` km/h, which may not precise by observing because there may be no significant differences when speed over 80km/h.
```{r}
# To show the bar chart using gender
latest_data %>%
  ggplot() +
    geom_bar(aes(x = gender, fill = gender)) +
  labs(title = "Distribution of Gender",
       subtitle = "Comparison of individuals by gender in the data",
       caption = "STATS 220 Project2",
       x = "gender",
       y = "count")

# To show the bar chart using licence
latest_data %>%
  ggplot() +
    geom_bar(aes(x = licence, fill = licence)) +
  labs(title = "Distribution of Licence",
       subtitle = "Comparison of individuals by licence ownership in the data",
       caption = "STATS 220 Project2",
       x = "licence",
       y = "total")
```

The above codes produce the comparisons and results by observing in daily life selected for this report.

The reason of data of average_speed by observing on the road may caused by individuals licence ownership.

There may be some bias in observations caused by their gender, because female is more sensitive than male in general.


